---
title: "Data Science Homework 6"
author: "Boya Guo"
date: "11/27/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(stats)
library(purrr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_bw())
set.seed(1)
```

### Problem 1
```{r read in data}
homicide = read_csv(file = "./data/homicide-data.csv") %>% 
  janitor::clean_names() 
```

First, we tidy the data, modifiy and change the variable names 
```{r p1.1}
homicide_1 = homicide %>% 
   mutate(victim_race = fct_relevel(ifelse(victim_race == "White", "white", "non-white"), "white"),
         victim_age = ifelse(victim_age == "Unknown", NA, as.integer(victim_age)),
         victim_sex = as.factor(victim_sex),
         city_state = paste(paste0(city, ","), state),
         resolved = as.numeric(disposition == "Closed by arrest")) %>% 
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  select(uid, victim_race, victim_age, victim_sex, city_state, resolved)
```

Next we create a logistic regression model for Baltimore and save the output of glm as an R object
```{r p1.2}
baltimore_logistic = homicide_1 %>%
  filter(city_state == "Baltimore, MD") %>% 
  glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) 

save(baltimore_logistic,file = "baltimore_logistic.RData") 

baltimore_logistic
```

Then, we applied broom::tidy and obtain the estimate and CI for the adjusted OR 
```{r p1.3}
baltimore_logistic %>% 
  broom::tidy() %>% 
    mutate(OR = exp(estimate),
           conf_low = exp(estimate - 1.96*std.error),
           conf_high = exp(estimate + 1.96*std.error)) %>% 
    filter(term == "victim_racenon-white") %>% 
    select(term, OR, conf_low, conf_high) %>% 
    knitr::kable(digits = 4) 
```
The OR estimate for solving homicides comparing non-white victims to white victims is 0.4406 and the true OR lies between 0.3129 and 0.6204.


Next step, we run glm for each of the cities and extract the adjusted OR with CI

To do this, we create a logistic function and then perform the logistic regression on all cities
```{r p1.4}
city_logistic = function(x){
    homicide_1 %>% 
    filter(city_state == x) %>% 
    glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())  %>% 
    broom::tidy() %>% 
    mutate(OR = exp(estimate),
           conf_low = exp(estimate - 1.96 * std.error),
           conf_high = exp(estimate + 1.96 * std.error)) %>% 
    filter(term == "victim_racenon-white") %>% 
    select(term, OR, conf_low, conf_high)
}

cities = 
  tibble(city_state = unique(homicide_1$city_state)) %>% 
  mutate(map(.x = unique(homicide_1$city_state), ~city_logistic(.x))) %>% 
  unnest

cities
```

Create a plot that shows the estimated ORs and CIs for each city
```{r p1.5}
cities %>% 
  ggplot(aes(x = reorder(city_state, OR), y = OR, colour = city_state)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high, width = 0.9)) +
  labs(
    title = "The estimated odds ratios and confidence intervals for solving homicides comparing non-white victims to white victims for each city",
    x = "City",
    y = "Odds Ratio and Confidence Interval"
    ) + 
  theme(legend.position = "right", axis.text.x = element_text(angle = 90, size = 7))
```

